Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-04-30 writeup/gz_hubble_data.tex

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. We also describe and employ a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.

@@

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{galaxies --- catalogs --- surveys}

@@

The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole. The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as gravitational tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's potential. For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms. This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, luminosity, black hole activity, size, and the relative ages of the stellar populations.

The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day. This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc. The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes. Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics taking place \citep[for a recent review see][]{con14}.

Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework. Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution. The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}. Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}. The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors. Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate down to at least $z\gtrsim$ \citep{gen14}.

@@

We describe the sample selection and creation of the images used for GZH in Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface and the collection of classifications. Section~\ref{sec:debiasing} outlines the process used to calibrate and ``debias'' the crowdsourced votes. Section~\ref{sec:results} gives the main results as a catalog, with several examples of how the data may be queried in Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.

@@

The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria, which we describe below. The majority of the images (as implied by the project name) are taken directly from \hst{} Legacy Surveys.

@@

\subsection{Summary of Hubble Legacy Survey Imaging}\label{ssec:legacy_surveys}

\begin{itemize}
\item \hubble{} ACS imaging for the All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. The strip was originally selected due to low extinction and Galactic/zodiacal emission, making it a prime target for multi-wavelength observations by space-based observatories. The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$. Images were in two bands, with exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two well-studied fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). Data including Hubble ACS images are referred to as GOODS-N and GOODS-S, respectively. ACS imaged the GOODS fields in 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each epoch vary by band, from 1050--2100~seconds. The \Bband{} images were completed in a single epoch at the beginning of the survey, but the \Vband, \iband, and \zband{} images were taken in five separate epochs separated by 40--50~days each. The ACS images are dithered to a pixel scale of 0.03~\arcsec/pixel and covers a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per field). The $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and 25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}28^\textrm{s}, \delta=+02^\circ12^\prime21^{\prime\prime}$. Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, as well as the space-based observatories. The \hst{} ACS data from COSMOS consists of 1 orbit with 2028~seconds per pointing in \Iband, consisting of 590 total pointings. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\% completeness magnitude for a galaxy with a half-light radius of $0^{\prime\prime}.50$ in \Iband{} is 24.7 mag.

\item The Galaxy Evolution from Morphologies and SEDS \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South. The GEMS data covers $\sim800$~arcmin$^2$, and surrounds the area covered by GOODS-S. Images from ACS in GEMS have 1 orbit per pointing for a total of 63~pointings. The exposure times are 2160 and 2286~seconds in \Vband{} and \zband{}, respectively. The image resolution has a pixel scale of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitudes for source detection are 25.7 AB in \Vband{} and 24.2~AB in \zband. 
\end{itemize}

@@

For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{bar12}. We selected all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

For galaxies in the ACS General Catalogue \citep[AEGIS, COSMOS, GEMS, 2-epoch GOODS;][]{gri12}, the color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively. We also apply a nonlinear mapping to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:

@@

\noindent We adopt a value of $b=3$ for the \hst{} images in \citet{gri12}.

Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when GZH was launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

By the time that the 5-epoch sets of GOODS data were put into GZH, coverage in four separate \hst{} bands had become publicly available. The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband in the blue channel, \Iband{} in the red channel, and \zband in the green channel. These images also had the speckled noise pixels decolorized.

The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH. For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}. This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0\arcsec.95 and 1\arcsec.05 \citep{tan07}.

The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The coadded Stripe~82 images were assembled from runs 106 and 206 in DR7 and generated as JPGs using the method of \citet{lup04}.

To address a number of images in which the sky noise was highly colored (which might have been a distraction to users), we apply a soft-edged object mask to the image that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky. This technique was applied only to the coadded Stripe~82 and the COSMOS images.

\subsection{Artificial AGN}

We also created a set of images designed to measure the effect of AGN on morphological classifications. Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic the effect of a strong bulge. The presence of an AGN is simulated by modeling the PSF for \hst{} and then inserting a bright source near the center of a real galaxy. For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images with different simulated AGN for each chosen host.

@@

Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}. This includes photometric parameters from both \sextractor{} and \galfit, such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions. \galfit{} also provides the parametric S\'{e}rsic index and effective half-light radius for the best-fit model. All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.

Redshifts for the GZH catalog are compiled from a variety of sources to include in the GZH catalog. For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt ACSGC$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.

For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift. We first prioritize spectroscopic redshifts; these are provided in the ACS-GC, 3DHST, and MUSYC catalogs. If a high quality spec-z exists in the ACS-GC. we use that, else 3DHST, else MUSYC. More 98\% of the matched spec-$z$'s are consistent at $\Delta z<0.001$; therefore, the priority order of selection makes no negligible difference in this sample. If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (ACS-GC, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, we provided a correction for redshift-dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

In the GZH samples, the redshift range is large enough that we expect to measure cosmological evolution of the types and morphologies of galaxies in the sample. As a result, the previous methods of correcting for redshift dependent bias will not work. In addition, the effects of band shifting will change the images even more across these redshift ranges. %Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.

In order to test and correct for the effects of redshift, we generated a set of calibration images. These images consist of the same galaxy as it would appear over a variety of redshifts. The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$. These images were classified in the Galaxy Zoo interface using the same classification scheme as the original \hst{} images.

@@

We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code. The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target minimum redshifts in \hst{} imaging.

@@

In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model. This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$). The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$). We ran \ferengi{} for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.

@@

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of the individual user. The combination of all such parameters forms a high-dimensional space, and we have insufficient data to measure their individual effects. Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): a galaxy's $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).

The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary correction factors. We assume that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:

@@

We use the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since we expect the correction being applied to vary as a function of the intrinsic galaxy properties. We restrict the galaxies that can be used to measure the calibration to those with data at the pivot redshift of $z=0.3$, non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).

>>>>

\begin{abstract}

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.

@@

\keywords{galaxies:structure --- galaxies:high redshift --- galaxies:evolution --- methods:data analysis --- catalogs}

@@

The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole. The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as gravitational tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's potential. For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms. This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.

The advent of larger telescopes in an increasing range of observable wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day. This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc. The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes. Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.

Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework. Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution. The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}. Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}. The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors. Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.

@@

The sample selection and creation of the images used for GZH is described in Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface and the collection of classifications. Section~\ref{sec:debiasing} outlines the process used to calibrate and ``debias'' the crowdsourced votes. Section~\ref{sec:results} gives the main results as a catalog, with several examples of how the data may be queried in Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.

@@

\subsection{Hubble Legacy Surveys}\label{ssec:legacy_surveys}

The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria. The majority of the data (as implied by the project name) are taken directly from \hst{} Legacy Surveys, all of which primarily use imaging from the Advanced Camera for Surveys (ACS). A summary of the key parameters is given in Table~\ref{tbl:gzh_numbers}.

@@

\begin{itemize}
\item The All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area was selected for a deep survey due to a combination of low extinction and low Galactic/zodiacal emission. The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$. The two ACS bands for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two separate fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{} ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S, respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each epoch vary by band, from 1050--2100~seconds. The \Bband{} images were completed in a single epoch at the beginning of the survey, but the \Vband, \iband, and \zband{} images were taken in five separate epochs separated by 40--50~days each. Images are dithered to a pixel scale of 0.03~\arcsec/pixel and cover a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and 25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}, \delta=+02^\circ12^\prime$. Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, in addition to space-based observatories. The ACS data for COSMOS consists of 1 orbit per pointing with an exposure time of 2028~seconds in \Iband; 590 total pointings are used to cover the entire field. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\% completeness magnitude for a galaxy with a half-light radius of $0.50^{\prime\prime}$ in \Iband{} is 24.7 mag.

\item The Galaxy Evolution from Morphologies and SEDs \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South. The GEMS data covers $\sim800$~arcmin$^2$, completely surrounding the area covered by GOODS-S. Images from ACS in GEMS have 1 orbit per pointing for a total of 63~pointings. The exposure times are 2160 and 2286~seconds in \Vband{} and \zband{}, respectively. The image resolution has a pixel scale of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitudes for source detection are 25.7 AB in \Vband{} and 24.2~AB in \zband. 
\end{itemize}

@@

In the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \galapagos{} \citep{bar12}. GZH includes all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

For galaxies in the ACS-GC, color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively. A nonlinear mapping is applied to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:

@@

\noindent The GZH images from \citet{gri12} use a value of $b=3$.

Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

By the time that the 5-epoch sets of GOODS data were put into GZH (in March 2015), coverage in four separate \hst{} bands were publicly available. The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the green channel. These images also had the speckled noise pixels decolorized.

The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH. For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}. This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec and 1.05\arcsec \citep{tan07}.

The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The coadded Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.

To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask is applied to the image that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky. This technique was applied only to the coadded Stripe~82 and the COSMOS images.

\subsection{Images with simulated nuclear point sources}

GZH also includes a set of images designed to measure the effect of active galactic nuclei (AGN) on morphological classifications. Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic or distort the identification of a bulge component. The presence of an AGN is simulated by modeling the PSF for \hst{} and then inserting a bright source near the center of a real galaxy. For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images with different simulated AGN for each host.

@@

Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}. This includes photometric parameters such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions drawn from both \sextractor{} and \galfit. \galfit{} also provides the parametric S\'{e}rsic index and effective half-light radius for the best-fit model. All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.

Redshifts for the GZH catalog are compiled from a variety of sources. For each galaxy, the primary redshift used for debiasing calculations (Section~\ref{sec:debiasing}) is in the $\tt Z\_Best$ column of Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the following algorithm is used to select the $\tt Z\_BEST$ quantity. This first priority is spectroscopic redshifts; these are provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A high quality spectroscopic redshift in the ACS-GC is the primary option; if none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$; therefore, the priority order of selection makes no negligible difference for the sample. If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

In the GZH samples, the redshift range is large enough that cosmological evolution of the types and morphologies of galaxies is expected for galaxies in the sample. As a result, the previous methods of correcting for redshift dependent bias will not work. In addition, the effects of band shifting will change the images even more across these redshift ranges. %Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.

In order to test and correct for the effects of redshift, GZH includes a set of calibration images. These images consist of the same galaxy as it would appear over a variety of redshifts. The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$. These images were classified in the Galaxy Zoo interface using the same classification scheme as the original \hst{} images.

@@

The GZH classifications include 288 unique galaxies originally generated from SDSS imaging and processed with the \ferengi{} code. The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target minimum redshifts in \hst{} imaging.

@@

In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model. This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$). The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.

@@

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of the individual user. The combination of all such parameters forms a high-dimensional space, and there are insufficient data to measure their individual effects. Instead, this method uses only two parameters intended to capture the bulk of the change in bias (based on GZ1/GZ2): the $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).

The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary correction factors. It is assumed that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:

@@

GZH uses the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties. The galaxies that can be used to measure the calibration are restricted to those with data at the pivot redshift of $z=0.3$, non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).
